Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2011-01-14 paper/main.tex
minor additions to section 5

The GPU ALM algorithm is written in CUDA and utilizes the CUBLAS libraries.  The algorithm is the same as the CPU algorithm except that we had to parallelize the GPU at an additional level.  The CPU portion of the code acts as a conductor, making calls to GPU functions in C, while the GPU portion does the computation.

@@

In this section, we benchmark the performance of MATLAB, BLAS MKL, and GPU Cuda implementations of the Primal ALM algorithm on synthetic data to find the point at which the GPU version runs faster than CPU versions.
To simply the benchmark, we cap the number of inner iterations at 50 and outer iterations at 5000 and run the algorithm to convergence.
CPU code was run on an Intel Dual Socket Quad Core with 8 gigs of DDR3 RAM.  GPU code was run on a GTX480
We ran the A matrix with different ratios between m:n from 10:1:5 for m:2000:25:8000 with an x vector of 10 percent sparsity.  Tolerance levels were empirically seen to allow best performance with the inner loop tolerance set at one order of magnitude lower than the outer loop tolerance.

@@

To generate a meaningful comparison between different hardware
architectures, we compare on a per-board basis:

For CPU implementations, the benchmark makes use of
as all of the cores in as many cpu's are present.

For GPU implementations, the benchmark makes the best use
of the entire GPU chip (most GPU boards have a single GPU chip).

>>>>

The GPU ALM algorithm is written in CUDA and utilizes the CUBLAS libraries.  The algorithm is similar to the CPU algorithm except that we had to parallelize the code at an additional level. The CPU portion of the code serves as the conductor, making calls to GPU functions and directing the flow of the code, while the GPU portion does all of the computation.

@@

In this section, we benchmark the performance of MATLAB, BLAS MKL, and GPU Cuda implementations of the Primal ALM algorithm on synthetic data to find at which point the GPU implementation runs faster than CPU implementation.
To simply the benchmark, we cap the number of inner iterations at 50 and outer iterations at 5000 and run the algorithm to convergence.
CPU code was run on an Intel Dual Socket Quad Core with 8 gigs of DDR3 RAM.  GPU code was run on a GTX480
We ran the A matrix with different ratios between m:n from 10:1:5 for m:2000:25:8000 with an x vector of 10 percent sparsity.  Tolerance levels were empirically seen to allow best performance with the inner loop tolerance set at one order of magnitude lower than the outer loop tolerance.

To generate a meaningful comparison between different hardware
architectures, we compare on a per-board basis:  For CPU implementations, the benchmark makes use of
as all of the cores in as many cpu's are present.  For GPU implementations, the benchmark makes the best use
of the entire GPU chip (most GPU boards have a single GPU chip).

@@
